---
title: "ggplot_demo"
output: html_notebook
---

intuitive data visualisations
ggplot grammar
Data
Layers
Scales
Coordinates
Faceting (similar to pivot table)
Themes 

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.


```{r}
# install.packages("here")
library("ggplot2")
library("here")

titatnic_data_path <- here("data", "titanic_dataset")
titanic <- read.csv(file.path(titatnic_data_path, "train.csv"), stringsAsFactors=FALSE)
View(titanic)
```

Class and survived are currently saved as integers, however it is not "ratio" data so it should be turned into a factor
Sex abd Embarked are strings and should also be factors
```{r}
titanic$Pclass <- as.factor(titanic$Pclass)
titanic$Survived <- as.factor(titanic$Survived)
titanic$Sex <- as.factor(titanic$Sex)
titanic$Embarked <- as.factor(titanic$Embarked)
```

```{r}
ggplot(titanic, aes(x=Survived)) + geom_bar()

```
```{r}
prop.table(table(titanic$Survived))

```
```{r}
ggplot(titanic, aes(x=Survived)) + 
  theme_bw() + 
  geom_bar() + 
  labs(y = "Passenger Count",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Sex, fill = Survived)) + 
  theme_bw() + 
  geom_bar() + 
  labs(y = "Passenger Count",
       title = "Titanic Survival Rates")

```


```{r}
ggplot(titanic, aes(x=Pclass, fill = Survived)) + 
  theme_bw() + 
  geom_bar() + 
  labs(y = "Passenger Count",
       title = "Titanic Survival Rates")

```
```{r}
ggplot(titanic, aes(x=Sex, fill = Survived)) + 
  theme_bw() +
  facet_wrap(~Pclass) +
  geom_bar() + 
  labs(y = "Passenger Count",
       title = "Titanic Survival Rates")

```
```{r}
ggplot(titanic, aes(x=Age)) + 
  theme_bw() +
  geom_histogram(binwidth = 5) + 
  labs(y = "Passenger Count",
       x = "Age (binwidth = 5)",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Age, fill = Survived)) + 
  theme_bw() +
  geom_histogram(binwidth = 5) + 
  labs(y = "Rand.rate",
       x = "Age (binwidth = 5)",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Survived, y = Age)) + 
  theme_bw() +
  geom_boxplot() + 
  labs(y = "Age",
       x = "Survived",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Age, fill = Survived)) + 
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_density(alpha = 0.5) + 
  labs(y = "Age",
       x = "Survived",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Age, fill = Survived)) + 
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_histogram(binwidth = 5) + 
  labs(y = "Age",
       x = "Survived",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Age, fill = Survived)) + 
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_histogram(binwidth = 5) + 
  labs(y = "Age",
       x = "Max recruits",
       title = "Titanic Survival Rates")

```

```{r}
ggplot(titanic, aes(x=Age, fill = Survived)) + 
  theme_bw() +
  facet_wrap(Sex ~ Pclass) +
  geom_histogram(binwidth = 5) + 
  labs(y = "Age",
       x = "Max recruits",
       title = "Titanic Survival Rates")

```